Creating importance plot

### 2020-08-14 Scripts_for_results/03_creating_annotation_specifc_barplots.Rmd
updated figures/tables

```{r}
badata_gm12878_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF.rds"))
    perfdata <- perfdata[[3]]
  }

@@

```{r}
badata_k562_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF.rds"))
    perfdata <- perfdata[[3]]
  }

@@

```{r}
badata_gm12878_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu.rds"))
    perfdata <- perfdata[[3]]
  }

@@

```{r}
badata_k562_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu.rds"))
    perfdata <- perfdata[[3]]
  }

@@

>>>>

```{r}
badata_gm12878_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF.rds"))
    perfdata <- perfdata[[3]]
  }

@@

```{r}
badata_k562_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF.rds"))
    perfdata <- perfdata[[3]]
  }

@@

```{r}
badata_gm12878_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu.rds"))
    perfdata <- perfdata[[3]]
  }

@@

```{r}
badata_k562_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu.rds"))
    perfdata <- perfdata[[3]]
  }

@@

#############################################

#Plotting

```{r}
ggplot(all_rfperfs_a_p, aes(x=Annotation, y=Performance, fill=Tool)) +
    facet_grid(. ~ Tool) +
    geom_bar(stat="identity") +
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75, size=1) +
    guides(fill=FALSE) +
    scale_fill_manual(values = c("blue", "red"))+
    theme_minimal() +
    theme_bw()+
    xlab("Genomic Class") + 
    ylab("Balanced Accuracy") + 
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    strip.text.x = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    legend.position = "bottom",
    plot.title = element_text(size=20))
```

### 2020-08-14 Scripts_for_results/04_creating_rfe_lineplot.Rmd
updated figures/tables

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

## LOLLIPOP

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

@@

>>>>

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_holdout.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ_mean <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))
rfeperchr_summ_med <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = median(BA, na.rm = TRUE),
                   PerformanceIQR = IQR(BA, na.rm = TRUE))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_holdout.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ_mean <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))
rfeperchr_summ_med <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = median(BA, na.rm = TRUE),
                   PerformanceIQR = IQR(BA, na.rm = TRUE))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_holdout_peakachu.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ_mean <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))
rfeperchr_summ_med <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = median(BA, na.rm = TRUE),
                   PerformanceIQR = IQR(BA, na.rm = TRUE))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_holdout_peakachu.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ_mean <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))
rfeperchr_summ_med <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = median(BA, na.rm = TRUE),
                   PerformanceIQR = IQR(BA, na.rm = TRUE))

@@

###########################

# Plotting

```{r}
rfeperchr_gm12878_5kb_arrowhead_med <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_gm12878_5kb_arrowhead_med.rds")
rfeperchr_gm12878_10kb_peakachu_med <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_gm12878_10kb_peakachu_med.rds")

rfeperchr_summ_gm12878 <- rbind.data.frame(rfeperchr_gm12878_5kb_arrowhead_med,rfeperchr_gm12878_10kb_peakachu_med)
rfeperchr_summ_gm12878$Tool <- c(rep("Arrowhead", nrow(rfeperchr_gm12878_5kb_arrowhead_med)),
                                 rep("Peakachu", nrow(rfeperchr_gm12878_10kb_peakachu_med)))

rfeperchr_k562_5kb_arrowhead_med <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_k562_5kb_arrowhead_med.rds")
rfeperchr_k562_10kb_peakachu_med <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_k562_10kb_peakachu_med.rds")

rfeperchr_summ_k562 <- rbind.data.frame(rfeperchr_k562_5kb_arrowhead_med,rfeperchr_k562_10kb_peakachu_med)
rfeperchr_summ_k562$Tool <- c(rep("Arrowhead", nrow(rfeperchr_k562_5kb_arrowhead_med)),
                                 rep("Peakachu", nrow(rfeperchr_k562_10kb_peakachu_med)))

ggplot(rfeperchr_summ_gm12878, aes(x=Variables, y=Performance, color=Tool)) + 
    geom_line(size=2,) +
    geom_point(size=4, position = position_dodge(.9)) +
    geom_errorbar(aes(ymin=Performance-(PerformanceIQR+.01), ymax=Performance+(PerformanceIQR+.01)), 
                  width=4, 
                  size=1,
                  position = position_dodge(.9)) +
    xlab("Number of top ranked annotations") +
    ylab("Cross-Validated BA") + guides(color=guide_legend(nrow=2))+
    scale_color_manual(name="Boundary Type", 
                       values=c("blue", "red"))+
    scale_x_continuous(breaks = c(2,4,8,16,32,52),
                       labels = c(2,4,8,16,32,52))+
    theme_minimal() +
    theme_bw()+
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          #strip.text.x = element_text(size = 15),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=15),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = c(.75,.1))
```

### 2020-08-14 Scripts_for_results/05_creating_importance_plot.Rmd
updated figures/tables

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))

## LOLLIPOP

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))

@@

>>>>

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_holdout.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}
rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS
rfe.set.mat <- t(apply(rfe.set.mat,1,rev))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_holdout.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}
rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS
rfe.set.mat <- t(apply(rfe.set.mat,1,rev))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_holdout_peakachu.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}
rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS
rfe.set.mat <- t(apply(rfe.set.mat,1,rev))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_holdout_peakachu.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}
rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS
rfe.set.mat <- t(apply(rfe.set.mat,1,rev))

@@

####################################

#Plotting

```{r}
rfe.set.mat <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/impmat_gm12878_5kb_arrowhead.rds")
rfe.set.mat <- rfe.set.mat[-13,]
rfe.set.mat <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/impmat_gm12878_10kb_peakachu.rds")

distance.col = dist(rfe.set.mat, method = "euclidean")
#cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "lightblue", "blue"))(ncol(rfe.set.mat))
#my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))

Heatmap(t(rfe.set.mat),
        col=my_palette,
        border=TRUE,
        cluster_rows=FALSE,
        clustering_distance_columns = "euclidean",
        clustering_method_columns = "complete", #"ward.D",
        show_row_names = FALSE,
        show_column_names = FALSE,
        show_column_dend = FALSE,
        column_names_gp=gpar(fontsize = 20),
        column_names_rot = 90,
        column_names_centered = FALSE,
        show_heatmap_legend = FALSE,
        heatmap_legend_param = list(title = "Predictive\nImportance"),
        rect_gp = gpar(col = "black", lwd = 1),
        column_dend_side = "bottom",column_names_side = "bottom")
